Can machine learning correct microwave humidity radiances for the influence of clouds?

### 2021-01-25 Article/ici_submm_cloudcorr.tex
updated sect 2.1.3, Patrick's suggestion

\subsubsection{Small Microwave Satellite}
%
\begin{table}[t]
	\caption{Specifications of SMS channels.}
	\label{tab:specifications_SMS}	
	\begin{tabular}{lrrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
				& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		SMS-1	&	176.31    & 2000	&	0.45	\\
		SMS-2	&	178.81    & 2000 	&	0.45\\
		SMS-3	&	180.31    & 1000 	&	0.64\\
		SMS-4	&	181.51    & 1000 	&	0.64 \\
		SMS-5	&	182.31    & \phantom{0}500  &	0.88 \\
		SMS-6  & 325.15$\pm$6.60    & 2800 	 &0.60\\
		SMS-7  & 325.15$\pm$4.10    & 1800    &0.75	\\
		SMS-8  & 325.15$\pm$2.40    & 1200    &0.92\\
		SMS-9  & 325.15$\pm$1.20    & \phantom{0}800  &1.12  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
The Small Microwave Satellite (SMS) is a hypothetical satellite which we consider to represent the type of sensors currently being considered for future missions. We assume it to be a single across-track scanning microwave radiometer with five 183\,GHz channels and four 325\,GHz channels. A brief summary of the  channel specifications assumed is provided in Table~\ref{tab:specifications_SMS}.

>>>>

\subsubsection{Small Microwave Satellite}
%
\begin{table}[t]
	\caption{Specifications of SMS channels.}
	\label{tab:specifications_SMS}	
	\begin{tabular}{lrrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
				& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		SMS-1	&	176.31    & 2000	&	0.45	\\
		SMS-2	&	178.81    & 2000 	&	0.45\\
		SMS-3	&	180.31    & 1000 	&	0.64\\
		SMS-4	&	181.51    & 1000 	&	0.64 \\
		SMS-5	&	182.31    & \phantom{0}500  &	0.88 \\
		SMS-6  & 325.15$\pm$6.60    & 2800 	 &0.60\\
		SMS-7  & 325.15$\pm$4.10    & 1800    &0.75	\\
		SMS-8  & 325.15$\pm$2.40    & 1200    &0.92\\
		SMS-9  & 325.15$\pm$1.20    & \phantom{0}800  &1.12  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}

The Small Microwave Satellite (SMS) is a hypothetical satellite which we 
introduce to represent the type of sensors currently being considered 
for future small missions carrying a single instrument. We assume it to 
be a single across-track scanning microwave radiometer. In this study, we 
assume five 183 GHz channels and four 325 GHz channels, and just ignore 
if the mission has additional channels at lower frequencies or not. A brief summary of the  channel specifications assumed is provided in Table~\ref{tab:specifications_SMS}.
